%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[scaled]{helvet} % Modern Sans-Serif font
\renewcommand\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://memoowi.site/}{\LARGE Misbachul Munir Al Haddad Alwi}} & Email: \href{mailto:megatenlike@gmail.com}{megatenlike@gmail.com}\\
  \href{https://memoowi.site/}{memoowi.site} & Mobile: \href{tel:+6288232220652}{+62 882-3222-0652} \\
  \href{https://github.com/memoowi}{github.com/memoowi} & Instagram: \href{https://instagram.com/me_moowi}{@me\_moowi} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
\small{Software Engineer with a strong foundation in building scalable full-stack web and cross-platform mobile applications using TypeScript, Next.js, Flutter, and Laravel. Proven ability to architect complex systems, including e-commerce platforms and Learning Management Systems. Leverages a unique background in technical instruction to bring strong communication, leadership, and mentorship skills to collaborative engineering teams.}
\vspace{-5pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Politeknik IDN Bogor}{Bogor, Indonesia}
      {Bachelor of Applied Science in Software Engineering; Current GPA: 3.72}{Aug 2023 -- Expected May 2027}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Programming Languages}{: Python, JavaScript, PHP, Dart}
     \hfill
     \textbf{Web Development}{: React.js, Next.js, Laravel}
   }
   \item{
     \textbf{Mobile/Cross-Platform}{: Flutter}
     \hfill
     \textbf{Database Management}{: SQL, Firebase, Supabase}
   }
   \item{
     \textbf{Cloud Platforms}{: Google Cloud}
     \hfill
     \textbf{Agile Methodologies}{: Scrum, Kanban}
   }
   \item{
     \textbf{Other}{: UI/UX Design}
     \hfill
     \textbf{Languages}{: Indonesian (Native), English (Proficient)}
   }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IDN Boarding School}{Bogor, Indonesia}
      {Software Development Teacher, Guide \& Treasurer}{Jul 2024 -- Jul 2026}
      \resumeItemListStart
        \resumeItemPlain{Delivered a comprehensive 2-year full-stack curriculum, teaching foundational to advanced web development (TailwindCSS, Laravel, React, Next.js) in the first year, and cross-platform mobile development (Flutter) in the second year.}
        \resumeItemPlain{Serving as a guide for the ``Backpacker 20 Countries'' program, coordinating international travel and educational activities.}
        \resumeItemPlain{Acting as the program treasurer, managing finances, budgeting, and resource allocation for the 1-year journey.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------LEADERSHIP & VOLUNTEER-----------------
\section{Volunteer Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Google Developer Student Club Widyatama}{}
      {Study Jam 7.0 Mobile Development Speaker}{Mar 2024}
      \resumeItemListStart
        \resumeItemPlain{Delivered an engaging mobile development workshop using Flutter with BLoC, focusing on techniques for consuming APIs.}
      \resumeItemListEnd

    \resumeSubheading
      {Polytechnic of IDN Bogor}{}
      {Flutter IT Camp Trainer}{Mar 2024}
      \resumeItemListStart
        \resumeItemPlain{Trained beginner participants in a 2-day online Flutter workshop, guiding them through building responsive food applications.}
        \resumeItemPlain{Showcased methodologies for developing applications compatible with multiple platforms.}
      \resumeItemListEnd

    \resumeSubheading
      {Polytechnic of IDN Bogor}{}
      {Front-end Bootcamp Trainer}{Dec 2023}
      \resumeItemListStart
        \resumeItemPlain{Led a 5-day intensive web development bootcamp, successfully transforming beginners into proficient users of HTML, CSS, JavaScript, and ReactJS frameworks.}
        \resumeItemPlain{Fostered a collaborative learning environment, emphasizing teamwork and practical, hands-on application.}
      \resumeItemListEnd

    \resumeSubheading
      {SMKN 1 Cibinong}{}
      {Web Development Learning Mentor}{Nov 2023}
      \resumeItemListStart
        \resumeItemPlain{Led a 1-week intensive web development course for over 25 high school students.}
        \resumeItemPlain{Covered fundamental web development concepts and conducted hands-on sessions focused on building responsive user interfaces.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DigiKelas}{Next.js, TS, Tailwind, Supabase}
      {Interactive web-based digital learning platform featuring e-modules and mini-games.}{}
      \resumeItemListStart
        \resumeItemPlain{Developed a client-server architecture utilizing Next.js App Router and Server Actions, integrated with Supabase.}
        \resumeItemPlain{Designed a structured learning path with pre/post-tests, interactive e-modules, and 6 interactive educational mini-games.}
        \resumeItemPlain{Engineered a gamification system featuring real-time leaderboards and automated graduation certificates.}
        \resumeItemPlain{Built a secure, child-friendly PIN-based authentication system alongside quiz time management and anti-cheat protections.}
      \resumeItemListEnd

    \resumeSubheading
      {InOut}{Flutter, Supabase, PostgreSQL}
      {Android application for managing device check-in and check-out tracking.}{}
      \resumeItemListStart
        \resumeItemPlain{Built a mobile-first Android application directly connecting to a Supabase backend for secure authentication.}
        \resumeItemPlain{Implemented fast QR-based check-in/out functionality with robust borrowing history tracking and activity monitoring.}
        \resumeItemPlain{Optimized data retrieval using indexed PostgreSQL queries with row-level security (RLS) for data isolation.}
      \resumeItemListEnd

    \resumeSubheading
      {GasNugas}{Next.js, TypeScript, Supabase, Cloudflare}
      {Role-based academic management system with structured workflows.}{}
      \resumeItemListStart
        \resumeItemPlain{Engineered a hybrid SSR/CSR application with role-based access control spanning Admin, Student, and Guardian portals.}
        \resumeItemPlain{Developed comprehensive assignment submission and approval workflows featuring detailed activity logs and penalty tracking.}
        \resumeItemPlain{Integrated Supabase for authentication and PostgreSQL operations, and Cloudflare R2 for efficient file edge delivery.}
        \resumeItemPlain{Designed a real-time class performance analytics dashboard and implemented a responsive Light/Dark mode UI.}
      \resumeItemListEnd

    \resumeSubheading
      {Hadirin}{Flutter, Firebase, ML Kit, Cloudinary}
      {Mobile attendance app with on-device face recognition and geo-fenced check-in.}{}
      \resumeItemListStart
        \resumeItemPlain{Implemented on-device face recognition via MobileFaceNet with face embeddings securely stored in Firestore.}
        \resumeItemPlain{Engineered geo-fenced check-ins with an admin-configurable radius for verifiable, location-aware records.}
        \resumeItemPlain{Integrated Cloudinary for hosting enrolled face images and developed role-based access control (admin/basic).}
        \resumeItemPlain{Designed a complete attendance history interface featuring face snapshots, GPS metadata, and persistent themes.}
      \resumeItemListEnd

    \resumeSubheading
      {mewTime}{Next.js, TypeScript, Supabase, PostgreSQL}
      {Self-service attendance platform for online classes.}{}
      \resumeItemListStart
        \resumeItemPlain{Built a session-based attendance system enabling lecturers to generate and share custom class codes mid-class.}
        \resumeItemPlain{Implemented a lecturer dashboard for comprehensive class session management and full attendance history tracking.}
        \resumeItemPlain{Developed a student portal for self check-in with live timestamps and secure authentication via Supabase Auth.}
      \resumeItemListEnd

    \resumeSubheading
      {Class of 2027}{Flutter, Firebase, Firestore}
      {Android attendance application for classroom roll calls and session reporting.}{}
      \resumeItemListStart
        \resumeItemPlain{Developed a daily roll call system with per-student status inputs (Present, Sick, Permission, Absent).}
        \resumeItemPlain{Designed session attendance reports with actionable features like "copy present NIS" and weekly recap generation.}
        \resumeItemPlain{Integrated Firebase Auth for secure teacher access, Cloud Firestore for student rosters, and Storage for profile photos.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}